%  Make this into a pdf document as follows:
%
%
% The edit the Report.tex file appropriately to include only those elements that
% make sense for the assignment you're reporting on.
%
% You can use a tool like TeXShop or Texmaker or some other graphical tool
% to convert Report.text into a pdf file.
%
% If you are making this with command line tools, you'd run the following command:
%
%     latex Report.tex
%
% That will generate a dvi (device independent) document file called Report.dvi
% The pages reported in the table of contents won't be correct, since latex only
% processes one pass over the document. To adjust the page numbers in the contents,
% run latex again:
%
%    latex Report.tex
%
% Then run
%
%   dvipdf Report.dvi
%
% to generate Report.pdf
%
% You can view this file to check it out by running
%
% xdg-open Report.pdf
%
% That's it.

\def\cvss(#1,#2,#3,#4,#5,#6,#7,#8,#9){
	\indent\textbf{CVSS Base Severity Rating: #9}  AV:#1 AC:#2 PR:#3 UI:#4 S:#5 C:#6 I:#7 A:#8}

\def\ttp(#1, #2, #3, #4, #5, #6){
	\indent\textbf{#1:} #2 \\
	\indent\indent\textbf{#3:} #4 \\
	\indent\indent\indent\textbf{#5:} #6 \\}

\documentclass[notitlepage]{article}

\usepackage{bibunits}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{datetime}
\usepackage{numprint}

% processes above options
\usepackage{palatino}  %OR newcent ncntrsbk helvet times palatino
\usepackage{url}
\usepackage{footmisc}
\usepackage{endnotes}

\setcounter{secnumdepth}{0}
\begin{document}
	
	\nplpadding{2}
	\newdateformat{isodate}{
		\THEYEAR -\numprint{\THEMONTH}-\numprint{\THEDAY}}
	
	\title{PenTest Lab Exercise Ex020 - OSInt}
	\author{Jonathan Trost}
	\date{\isodate\today}
	
	\maketitle
	
	\tableofcontents
	
	\newpage
	\section{Attack Narrative}
	
	\subsection{KEY003}
	To start, with the clues given I googled the venue in order to see what concerts had been played there. I found the venue's facebook page. There were only a few shows listed. I began copying all concert posts.  I saw the words 'king of bleeps and ruler of the bloops' which I assumed would be chiptunes.  From there I found \textbf{Melt Channel's} twitter and sound cloud page finding the track \textbf{Island}. The track was released on the 8 Dec 2015 album. Using \textbf{Island} I got the following:   \\
	The result is KEY003-F4D3onyBkoYdCzBcFrihpA== \\
 
	\subsection{KEY004}
	The twitter for \textbf{Melt Channel} listed in one of its' last posted that it was becoming \textbf{Magic Circuit}. I assumed that this was the hinted at change in projects by person X. I then reviewed \textbf{Magic Circuit's} albums and found a album released on the correct date featuring several vocalists. Track 6 on that album is \textbf{Living Underwater feat. Gina}.  Using \textbf{Gina} as the code gave me the following: \\
	The result is KEY004-jfHIhklfispmr7p8HJ7Jew== \\
	
\end{document} 