%  Make this into a pdf document as follows:
%
%
% The edit the Report.tex file appropriately to include only those elements that
% make sense for the assignment you're reporting on.
%
% You can use a tool like TeXShop or Texmaker or some other graphical tool
% to convert Report.text into a pdf file.
%
% If you are making this with command line tools, you'd run the following command:
%
%     latex Report.tex
%
% That will generate a dvi (device independent) document file called Report.dvi
% The pages reported in the table of contents won't be correct, since latex only
% processes one pass over the document. To adjust the page numbers in the contents,
% run latex again:
%
%    latex Report.tex
%
% Then run
%
%   dvipdf Report.dvi
%
% to generate Report.pdf
%
% You can view this file to check it out by running
%
% xdg-open Report.pdf
%
% That's it.

\def\cvss(#1,#2,#3,#4,#5,#6,#7,#8,#9){
	\indent\textbf{CVSS Base Severity Rating: #9}  AV:#1 AC:#2 PR:#3 UI:#4 S:#5 C:#6 I:#7 A:#8}

\def\ttp(#1, #2, #3, #4, #5, #6){
	\indent\textbf{#1:} #2 \\
	\indent\indent\textbf{#3:} #4 \\
	\indent\indent\indent\textbf{#5:} #6 \\}

\documentclass[notitlepage]{article}

\usepackage{bibunits}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{datetime}
\usepackage{numprint}

% processes above options
\usepackage{palatino}  %OR newcent ncntrsbk helvet times palatino
\usepackage{url}
\usepackage{footmisc}
\usepackage{endnotes}

\setcounter{secnumdepth}{0}
\begin{document}
	
	\nplpadding{2}
	\newdateformat{isodate}{
		\THEYEAR -\numprint{\THEMONTH}-\numprint{\THEDAY}}
	
	\title{PenTest Lab Exercise Ex050 - nmap}
	\author{Jonathan Trost}
	\date{\isodate\today}
	
	\maketitle
	
	\tableofcontents
	
	\newpage
	
	\subsection{Summary of Findings}
	\indent Pr0b3 performed reconnaissance on Art's Tailor shops network to find open ports and services running. A vulnerability scan was performed on the active services. One of the running services was found to have a  serious exploit that requires corrective action.  
	
	\subsection{Finding: \emph{Backdoor on File Transfer Server, vsftpd 2.3.4}}
	
	\subsubsection{Severity Rating}
	The severity is 9.8. This is a high risk exploit that opens a shell on the root on the machine.  This exploit would allow the attacker to take data, delete data, and bring down the system or install additional tools.  

	\textbackslash cvss(N,L,N,N,U,H,H,H,9.8)\\
	\cvss(N,L,N,N,U,H,H,H,9.8) \\
	
	\subsubsection{Vulnerability Description}
	The vulnerability opens a shell on port 6200/tcp. This allows the user to perform any actions on the system a user could. The attacker could access secure files, delete data, or bring down the system. This vulnerability has a high impact for confidentiality, integrity, and availability of th system and data. 
	
	\subsubsection{Confirmation method}
	To confirm the exploit: \\
	\indent 1. In command line type \textbf{nmap -sT www.artstailor.com}.\\
	\indent 2. Under PORT 21, you will see the service \textbf{ftp} with version \textbf{vsftpd 2.3.4}. \\
	\indent 3. In command line type \textbf{searchsploit vsftpd 2.3.4} \\
	
	
	\subsubsection{Mitigation or Resolution Strategy}
	Download and use the latest version of vsftpd. The back door and been removed. \\
	
	\section{Attack Narrative}
	A TCP and UDP scan of www.artstailor.com with \textbf{nmap} was performed.  The TCP scan performed the default 1000 port scan and the UDP scan was limited to 1-256 for the most commonly used ports. The UDP scan does take much more time. \\
	The active TCP ports were port 21 for connection to file transfer system. port 22 for SSH, port 53 for domain name service, and port 80 for http.  These 4 parts are active and performing the normal tasks for these port numbers. \\
	The only abnormal port was UDP port 40. The service was blocked or filtered by the firewall. The service port 40 is unknown. This port does not have a normal service usually performed in the way that port 21, 22, 53, and 80 do. \\ \\
	A key was found among ICMP packets: 
	\textbf{KEY007-Smnqzo/vG7UTSS1fTTUW7g==} \\
	
	\subsection{MITRE ATT{\&}CK Framework TTPs}
	
	\indent\textbackslash ttp(T0043, Reconnaissance, T1595, Active Scanning, .002, Vulnerability Scanning) \\
	
	\ttp(TA0043, Reconnaissance, T1595, Active Scanning, .002, Vulnerability Scanning) \\

\end{document} 