%  Make this into a pdf document as follows:
%
%
% The edit the Report.tex file appropriately to include only those elements that
% make sense for the assignment you're reporting on.
%
% You can use a tool like TeXShop or Texmaker or some other graphical tool
% to convert Report.text into a pdf fi le.
%
% If you are making this with command line tools, you'd run the following command:
%
%     latex Report.tex
%
% That will generate a dvi (device independent) document file called Report.dvi
% The pages reported in the table of contents won't be correct, since latex only
% processes one pass over the document. To adjust the page numbers in the contents,
% run latex again:
%
%    latex Report.tex
%
% Then run
%
%   dvipdf Report.dvi
%
% to generate Report.pdf
%
% You can view this file to check it out by running
%
% xdg-open Report.pdf
%
% That's it.

\def\cvss(#1,#2,#3,#4,#5,#6,#7,#8,#9){
	\indent\textbf{CVSS Base Severity Rating: #9}  AV:#1 AC:#2 PR:#3 UI:#4 S:#5 C:#6 I:#7 A:#8}

\def\ttp(#1, #2, #3, #4, #5, #6){
	\indent\textbf{#1:} #2 \\
	\indent\indent\textbf{#3:} #4 \\
	\indent\indent\indent\textbf{#5:} #6 \\}

\documentclass[notitlepage]{article}

\usepackage{bibunits}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{datetime}
\usepackage{numprint}

% processes above options
\usepackage{palatino}  %OR newcent ncntrsbk helvet times palatino
\usepackage{url}
\usepackage{footmisc}
\usepackage{endnotes}
\usepackage{hyperref}

\urlstyle{same}

\setcounter{secnumdepth}{0}
\begin{document}
	
	\nplpadding{2}
	\newdateformat{isodate}{
		\THEYEAR -\numprint{\THEMONTH}-\numprint{\THEDAY}}
	
	\title{PenTest Lab Exercise Ex0d0 - Books is Breached}
	\author{Jonathan Trost}
	\date{\isodate\today}
	
	\maketitle
	
	\tableofcontents
	
	\newpage 
	
		\subsection{Summary of Findings}
	\indent Pr0b3 used the employee information previously collected to access an internal computer. Based on an overhead conversation pr0b3 was able to determine that the \textbf{sticky keys} could be used to gain access to a command line with root privileges. 
	
	\subsection{Finding: \emph{Windows CNG Key Isolation Service Elevation of Privilege Vulnerability CVE-2022-41125}}
	
	\subsubsection{Severity Rating}
	\indent The severity is 7.8 
	
	\textbackslash cvss(L,L,L,N,U,H,H,H,7.8)\\
	\cvss(L,L,L,N,U,H,H,H,7.8) \\
	
	\subsubsection{Vulnerability Description}
	\indent Someone on customers staff has setup the sticky keys exploit to allow them to perform a password reset when convenient. This exploit allows another person with access to the computer to open a command line wiht root privileges.  \\
	
	\subsubsection{Confirmation method}
	To confirm the exploit use: \\
	\indent 1. Log into books.artstailor.com and type \textbf{\\reset} into the windows search box and press enter.  \\
	\indent 2. Log out and log back in to computer. \\
	\indent 3. Press shift fives times.  Once sticky keys window pops up, click on the accessibility button in bottom left. \\
	\indent 4. A command line should be started with root privileges that does not require logging into the computer. 
	
	\subsubsection{Mitigation or Resolution Strategy}
	\indent Remove the \textbf{reset.bat} file and doe not allow users with admin privileges to perform this exploit. Restrict admin rights to most employees.  
	
	\section{Attack Narrative}
	\indent I used the method described in report Ex0b0 to gain access to boosk.artstailor.com. I then searched the file system and found the reset.bat file at the to of the \textbf{C:\\\\} directory. I then ran the \textbf{//reset} command in the windows search bar. I logged out of \textbf{books.artstailor.com} and then went to the login screen. I then pressed the shift key 5 times. Once the sticky keys prompt came up, I selected the accessibility settings. This caused the command line with root privileges to start.  I then searched through the file system and found the "creds" file within a.turning files system. Inside the creds file I found what I suspect are passwrods for a.turning for: Gatorlink, Amz, Schwab, Insta, TikTok, FB, Windows, Linux, and game. \\ 
	
	
	 A key was found in A.turning cred file. \\

	The code was \textbf{KEY014-qf/UZuKos+DzV6ot0Tktjg==} \\
	
	\subsection{MITRE ATT{\&}CK Framework TTPs}
	
	\indent\textbackslash ttp(TA0004, Privilege Escalation, T1548, Abuse Elevation Control Mechanism, .002, Abuse Elevation Control Mechanics: Bypass Account Control) \\
	\ttp(TA0004, Privilege Escalation, T1548, Abuse Elevation Control Mechanism, .002, Abuse Elevation Control Mechanics: Bypass Account Control) \\


\end{document} 